PROTEST

### 2019-09-04 article/main.tex
article: dg section

  \item We then calculated the proportion of $G_{fir}$ for all conifer mixtures over the study area by adding to the model predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the model residuals. $G_{spruce}$ was obtained by substracting $G_{fir}$ to $G_t$.

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate and $\varepsilon$, the model residuals. Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area, and this, before the grouping of species. We applied the same variable selection procedure as the one we applied to the site index model (see the three final models in SI).

  \item We then calculated $r_{Dg}$, the $Dg_i / Dg_j$ ratios for all mixed stand over the study area by adding to the models predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals.

@@

  \begin{equation}\label{}
    Dg_j = \frac{Dg_i}{a}
  \end{equation}

@@

--> on s'est assuré que les a et b soient dans un interval de valeur défini

>>>>

  \item We then calculated $P_{Gfir}$, the proportion of $G_{fir}$ for all conifer mixtures over the study area by adding to the model predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the model residuals. We made sure that $0.25 < P_{Gfir} < 0.75$ to comply with the definition of mixture that we use in this study. Another random number was drawn and added to the model prediction until this condition was met. $G_{spruce}$ was then obtained by substracting $G_{fir}$ to $G_t$.

@@

  where $Dg_i$ and $Dg_j$ are the quadratic diameters of species $i$ and $j$; $\alpha$ and $\beta_{1-X}$, parameters to estmiate; and $\varepsilon$, the model residuals. Here, we used $Dg_i$ and $Dg_j$ obtained from "true mixtures", i.e. PROTEST plots where the two mixed species represented more than 75\% of the total basal area, and this, before the grouping of species. We applied the same variable selection procedure as the one we applied to the site index model (see the three final models in SI).

  \item We then calculated $r_{Dg}$, the $Dg_i / Dg_j$ ratios for all mixed stand over the study area by adding to the models predictions a random number drawn from the normal distribution $\mathcal{N} (0, \sigma_\varepsilon)$, with $\sigma_\varepsilon$ being the standard deviation of the models residuals. We made sure that $r_{Dg}$ falled in the range of the $Dg_i / Dg_j$ ratio values directly measured in the PROTEST "true mixtures" to avoid producing stands with unbalanced diameters for both species. Another random number was drawn and added to the models predictions until this condition was met.

@@

  \begin{equation}\label{}
    Dg_j = \frac{Dg_i}{r_{Dg}}
  \end{equation}

@@
